\section{Privacy}\label{sec:priv}
In this section we analyze some of the tools which focus on privacy and
anonymity for average users. Specifically we examine the problems of contact
discovery (how to users of a service discovery whether contacts also use a
service), presence discovery (whether users are currently online), and anonymous
communication.

\subsection{Private Information Retrieval}\label{ssec:PIR}
We briefly introduce the notion of Private Information Retrieval (PIR) as it
crops up in many of the future topics. There are two main classes of PIR,
Information Theoretic (IT-PIR) and Computational (C-PIR). Private information
retrieval was introduced in~\cite{chor1995private} as a means of querying a
database without explicitly informing the server which element was queried.

As is common with privacy schemes there is a simple naive approach: the client
requests the entire database and locally searches for the desired entry. Of
course this method of PIR is infeasible. There has been numerous work in
providing useable and efficient PIR with acceptable threat models
usable~\cite{aguilar2016xpir,devet2012optimally,beimel2002robust} as well as
providing implementations of uses of PIR, such as PIR-Tor~\cite{mittal2011pir}
which provides an implementation of Tor to gain information on Tor nodes from a
small subset of onion routers using PIR as opposed to using a Peer-to-Peer
network.

\subsubsection{Information Theoretic Private Information Retrieval}
IT-PIR focuses on solving the problem of private database look-ups by
introducing multiple non-colluding servers. These schemes have multiple
(sometimes partial) copies of the database on multiple servers. The client then
constructs specific queries to each server and combines the results.

For example, a client interested in the 3rd entry of a database may make a
request for the \texttt{xor} of the 3rd, 10th and 25th entries of the database
from one server and the \texttt{xor} of the 10th and the 25th entries of the
database from a second server. Locally the client can \texttt{xor} the  replies
from the servers to obtain the 3rd entry. As long as the servers do not discuss
what was requested from each neither knows what entry was actually desired.

Recent work~\cite{demmler2018pir} leverages Distributed Point Functions which
enables querying over the full database in a quick (but private) way.

Previous work has also examined how robust IT-PIR is both in terms of server
failure~\cite{beimel2002robust} and in terms of malicious
servers~\cite{devet2012optimally} to still provide functionality when a
threshold of servers are either purposely non-responsive, or malformed
responses.

\subsubsection{Computation Private Information Retrieval}
\computationalPIR

C-PIR allows for private database queries by leveraging homomorphic encryption. Homomorphic encryption has an encryption function $E(\cdot)$, and decryption function $D(\cdot)$ with the following property:
\[
    D(E(a) + E(b)) = a + b
\]
This allows for querying from a database privately as demonstrated in
Figure~\ref{fig:cpir}. The client can create a vector of encryptions of 0s and a
1 in the location of the entry of the desired file. Upon receiving this
encrypted query the server can use homomorphic multiplication (repeated addition
$D(c\cdot E(a)) = c\cdot a$) and the homomorphic addition property to return the
requested file while learning nothing of \textit{which} file was requested.

Unfortunately C-PIR is computationally expensive, often to the point of infeasibility for practical use. Though previous work~\cite{aguilar2016xpir,dong2014fast,gentry2005single} has attempted to develop and implement efficient C-PIR any current close to practical protocol limits the size of the database queried in C-PIR, or uses C-PIR in conjunction with other privacy preserving methods (such as Private Set Intersection~\cite{freedman2004efficient}).

\subsection{Contact discovery}\label{ssec:contactDiscovery}
Contact discovery is the process of clients of a service discovering whether any
of their contacts also use the same service.

In non-private settings this is very simple to achieve, the client provides
contact details to the service which then queries its database and returns who
is available on the service. This method requires each client to reveal their
whole contact list to the service. Allowing the service to track metadata on
every client, as well as leaking non-clients phone numbers.

Signal systems has gone through the process of trying to handle contact
discovery in a private way~\cite{marlinspike_2014}. As a text messaging service
offering end-to-end encryption it is necessary for Signal to be aware of which
contact are also Signal clients. They address the difficulties of contact
discovery, a natural first attempt is to simply hash contacts and send them to
the service to verify hashes. Unfortunately the pre-image space of these hashes
is small (there are only 10 billion possible phone numbers, many of which are
not valid, due to area codes) which allows to off-line attacks by the service
after receiving a client's contact list. Other possible options for contact
discovery exist including using Private Information Retrieval (PIR), bloom
filters, and Private Set Intersection (PSI), though these solutions cause
services to make trade-offs due to either large overhead in communication sizes
or in computation costs. Signal has recently implemented a more private contact
discovery method leveraging Intel's Software Guard Extensions
(SGX)~\cite{marlinspike_2017}. The high-level implementation is that clients
make a secure connection to the Signal server and perform a remote attestation
that the code they are running is the published open-source code, and then use
SGX's trusted enclave to perform an intersection where the server is sent an
encrypted form of the clients contacts (which are only decrypted and readable in
the trusted enclave). 

However, recent attacks on SGX~\cite{van2018foreshadow} have demonstrated the
the trusted enclave should not be so trusted. This leads to the natural question
of ``are there better methods of contact discovery?''. 

As stated above, the use of PIR or PSI as a method of private contact discovery
has large overhead which is not usable for large services. However, recent
work~\cite{demmler2018pir} has combined these two concepts to lessen the
overhead. Using a distributed point function, clients can generate an
information theoretic private information retrieval (IT-PIR) request from 2-4
separate servers, afterward this request is completed by using a Private
Equality Test (PEQ) between the client's contact information and the database
query. This method scales better than previous methods in that a client with
1024 contacts can perform private contact discovery with a server of 67 million
clients in 1.36 seconds and 4.28MiB of communication.

\subsection{Presence discovery}
Presence discovery is the concept a client of a service discovering whether any
of their ``friends'' or contacts on the services are currently online. Again
naively, this can be done by simply requesting information on each contact,
which leaks metadata.

This can be done privately with PIR, but as expected this does not scale well.
The threat model here is generally that only your friends should be able to
query about your online status and you should not have to announce your friends.

% talk about DP5 in more detail
DP5~\cite{borisov2015dp5} has found ways to make PIR scale more effectively. By
breaking up the size of the database that must be queried PIR methods can still
be effectively used. DP5 works by having a user upload an identifier and a
single symmetric key encrypted under a different public key for each ``friend''
on their contact list to a long-term key database (on the order of a day).
Additionally a single entry (containing online status) encrypted under the
common symmetric key is store in a short-term database (updated every few
minutes). 

The short-term database only has at most one entry per user, which allows for
effective use of IT-PIR. The long-term database contains many entries per user
which scales poorly with PIR, fortunately it only needs to be queried at most
once per day, making the costs not too prohibitive. 

The dual nature of the ``online status'' of clients allows for certain
trade-offs, while the queries can be done privately and (relatively)
efficiently, removing friends can only be done on the order of the long-term
database. As online status is encrypted under a single symmetric key for all of
a clients friends, this status is available to all people that receive an entry
in the long-term database.

\subsection{Anonymous communication}\label{sec:anonymousCommunication}
Free communication is the backbone of freedom. Unfortunately not everyone has
the freedom of speech, and have the need to speak anonymously to avoid
persecution. Even those with freedom of speech often find the need to speak
anonymously.

There are tools which allow for anonymous communication such as
Tor~\cite{syverson2004tor} which provide anonymity by routing traffic through
relay nodes using onion routing. While the theoretic security provided is high
there are drawbacks such as vulnerability to traffic analysis and the need to
rely on enough volunteers so that a malicious adversary does not gain majority
control of the network. 